Water, Methane Depletion, and High-Altitude Condensates in the Atmosphere of the Warm Super-Neptune WASP-107\lowercase{b}

### 2018-02-22 ApJL_submission/ms.tex
response2

\subsubsection{Methane Abundance}
We ran two additional retrievals to explore whether methane depletion is the underlying cause of the inferred low C/O.  Even though water is the dominant absorber in the WFC3 bandpass, there is enough methane opacity to change the shape of the spectral features at a detectable level for high precision data.  In one test, we assumed chemical equilibrium but excluded methane opacity. This set-up resulted in a much broader distribution of C/O values ($0.02 - 1.6$ at $1\,\sigma$).

We also performed a ``free" retrieval that varied the abundances of CH$_4$, H$_2$O and NH$_3$ with no assumption of chemical equilibrium. The $3\,\sigma$ upper limit on methane abundance is $1.2\times10^{-3}$, ruling out the the predicted methane content for a composition with solar C/O and $3\,\times$ solar metallicity (the median metallicity from the chemical equilibrium retrieval).  Based on these tests, we conclude that the atmosphere of WASP-107b is depleted in methane relative to expectations for a solar abundance pattern. By contrast, the water abundance ($6\times10^{-6} - 2\times10^{-3}$) is consistent with predictions for solar composition.

>>>>

\subsubsection{Methane Abundance}
We ran two additional retrievals to explore whether methane depletion is the underlying cause of the inferred low C/O.  Even though water is the dominant absorber in the WFC3 bandpass, there is enough methane opacity to change the shape of the spectral features at a detectable level for high precision data.  In one test, we assumed chemical equilibrium but excluded methane opacity. This set-up resulted in a much broader distribution of C/O values ($0.02 - 1.6$ at $1\,\sigma$). \added{We infer from this test that the absence of methane is what drives the low retrieved C/O ratio.}

We also performed a ``free" retrieval that varied the abundances of CH$_4$, H$_2$O and NH$_3$ with no assumption of chemical equilibrium. The $3\,\sigma$ upper limit on methane abundance is $1.2\times10^{-3}$, \added{ruling out the predicted equilibrium methane content at the base of the cloud deck ($1.4\time10^{-3}$ at 700 K, 10 mbar, for a solar C/O and $3\,\times$ solar metallicity composition).}  We chose $3\times$ solar as a benchmark for comparison because this is the median metallicity from the chemical equilibrium retrieval; \added{however, we note that the expected equilibrium abundance is sensitive to the true atmosphere metallicity. For a $1\times$ solar composition, the expected methane abundance drops by $1/3$. Similarly, the expected abundances are sensitive to the temperature and pressure in the photosphere. For example, at slightly higher temperatures and higher altitudes (1 mbar, 800 K), the expected methane abundance drops to $2.4\times10^{-5}$.}  Based on these tests, we conclude that the atmosphere of WASP-107b is \added{likely} depleted in methane relative to expectations for a solar abundance pattern. By contrast, the water abundance ($6\times10^{-6} - 2\times10^{-3}$) is consistent with predictions for solar composition. FIXME
